Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-08-13 Paper/gammaRays.tex
Corrections to Photon observation time

Out of 19 bursts studied, only 4 have at least 10 high energy events remaining after filtering, and thus eligible for the computation of stretching factors. The results of this computation are shown on figures \ref{fig:grb080916C}, \ref{fig:grb090510}, \ref{fig:grb090902B}, \ref{fig:grb090926A} and table \ref{tab:observationResults}.

@@

GRB 090926A has, however, high energy radiation stretched with respect to low energy signal (that is $\kappa > 1$). In contrast to that, GRB 090902B has low energy radiation stretched with respect to high energy signal ($\kappa < 1$).

@@

Note that $\tau$ doesn't depend on $d$ anymore. But this is only true if the scale factor did not change from emission to observation. For a distant observer we should account for the change in the scale factor, which will stretch the distances between photons:
\begin{equation}
\tau \left(r, \theta, \phi, z, \chi \right) = r\left( \frac{1}{v} - \cos\sigma\left( \theta, \phi, \chi \right) \right) \left( 1 + z \right)
\end{equation}
Here $z$ is the redshift of the burst from the point of view of the observer.

>>>>

Out of 19 bursts studied, only 4 have at least 10 high energy events remaining after filtering, and thus eligible for computating the stretching factors. The results of this computation are shown on figures \ref{fig:grb080916C}, \ref{fig:grb090510}, \ref{fig:grb090902B}, \ref{fig:grb090926A} and table \ref{tab:observationResults}.

@@

GRB 090926A has, however, high energy radiation stretched with respect to low energy radiation (that is $\kappa > 1$). In contrast to that, GRB 090902B has low energy radiation stretched with respect to high energy radiation ($\kappa < 1$).

@@

Note that $\tau$ doesn't depend on $d$ anymore. But this is only true if we did not account for cosmology, or if the scale factor did not change from emission to observation. For a distant observer it will change, however, which will stretch the distances between photons:
\begin{equation}
\tau \left(r, \theta, \phi, z, \chi \right) = r\left( \frac{1}{v} - \cos\sigma\left( \theta, \phi, \chi \right) \right) \left( 1 + z \right)
\end{equation}
Here $z$ is the redshift of the burst from the point of view of the observer.
